Self-tunable approximated explicit MPC: Heat exchanger implementation and analysis

### 2023-07-25 paper/JoPC/main.tex
polytopic partitions added

The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions. The corresponding polytopic partitions can be seen in Fig.~{ref} and Fig.~{ref}. To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required. Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.

@@

>>>>

The explicit MPC corresponding to the penalty matrix $Q_\mathrm{y, U}$ contains 1\,680 critical regions, and the explicit MPC with the penalty matrix $Q_\mathrm{y, L}$ contains 409 critical regions. The corresponding polytopic partitions can be seen in Fig.~\ref{fig:partition_U} for the upper boundary controller and Fig.~\ref{fig:partition_L} for the lower boundary controller. To store the parametric solution associated with the upper boundary explicit MPC, 17.49 MB of memory space is required. Storing the lower boundary explicit MPC, one needs 4.33 MB of memory space.

\begin{figure}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{images/partition_U}
		\caption{Polytopic partition of the upper boundary explicit MPC.}
		\label{fig:partition_U}
	\end{center}
\end{figure}

\begin{figure}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{images/partition_L}
		\caption{Polytopic partition of the lower boundary explicit MPC.}
	\label{fig:partition_L}
\end{center}
\end{figure}

@@

The control input is applied to the system each second, so there is a possible concern regarding the speed at which two explicit MPCs are evaluated. By analyzing the computational speed, it was concluded that the approximate control input can be generated in an average time of 0.01 seconds, which is 100 times faster than the sampling time.
